---
title: "W_UP_01"
author: "Carmen Ramos-Caminos"
date: "Summer2022"
output: html_document
---



The report structure should include five sections.  see below



```{r include=FALSE,echo=FALSE}
require(tigerstats)
require(tidyverse)
mydata <- read.csv(file="pushups.csv")
```

# Introduction  
<!--In this section you explain what you are trying to show. Where did the data come from? What is the research or other question you are trying to answer?!-->

Create an Rstudio project in your shared space on rstudio.cloud.  Using the dataset called pushups from the tigerstats package in R; answer the question posed by this null and alternate hypothesis in an html markdown document.

$H_0$: There is no difference between the average number of pushups of line vs skill players

$H_A$: The average number of pushups done by line players is statistically different than that of skill players. 

# Methods  
<!--Decide on your methods: use "variable analysis" or other appropriate descriptors. Make sure to choose at least one graphical method and at least one numerical method.!-->    
Position is a categorical variable. Push ups is a numerical variable. I will do an analysis that explains push ups based on position.  

# Results  
<!--Divide this section into two sub-sections: One for your descriptive results and one for your inferential results.!-->

## Descriptive Results

### Graphical Descriptive Results

<!--Graphical results here. Make sure to show your code. Provide appropriate labels for axes, giving units if possible, and provide a good title for the graph, too. Use the graphical results to describe the patterns if any that exist in the data as focused toward the research question!-->
```{r}
boxplot(pushups~position,data=mydata)
```
  
The Whisker Box plot for the Line position shows that line man perform pushups with a low 6 pushups and a high of 34 pushups.The Range is 34-6 equals a 28 push up differnce from high to low.  The Skill position players perform push ups with a low 18 pushups and a high of 90 push ups and one outlier at  108 pushups. The Range is 108-18 equals a 90 pushup difference from high to low. When comparing the Line players and Skill players the range is 6 low and 108 high. That is a Range differnce of 102 push ups. 
### Numerical Descriptive Results   
<!--Numerical results go here. Use the numerical results to describe the patterns if any that exist in the data as focused toward the research question!-->  
```{r}
favstats(pushups~position,data=mydata)
```
There is not much difference in the low push numbers up for either the Line player or the Skilled player. However, there is a major Range difference betweeen the max in Q4 of the Skilled position. The Whisker plot shows that both Line and Skilled Players performed more push ups the top half, that is  Q3 and Q4  closer to the higher end of the push up spectrum. 
 

## Inferential Results  
<!--State hypothesis clearly. Make sure your discussion of the inferential test covers all the aspects that the test output produces, such as test statistic, p-value etc. Make a decision about the null hypothesis, explain the assumptions on which the selected test/procedure was based, and why the chosen procedure satisfys the assumptions and is appropriate to answer the research question!-->     

  
```{r}
t.test(pushups~position,data=mydata)
```
Yes there is a difference between the average number of pushups performed  by line players with a mean of 14.5. It is statistically different than that of skill players with a mean of 47.5 with the P-value  0.000009421 less than zero.   

# Discussion and Conclusion  
<!--Discussion and conclusion here. If you found a relationship be sure to consider whether the relationship occurs because one of the variavbles causes the other, or whether they perhasps are related for some other reason. Watch the chapter 6 videos from the GeorgeTown videos collection.!-->

I reject the $H_0$: that there is no difference between the average number of pushups of Line player vs Skkill player. There is a significant difference in weight between the Line and Skilled players on the foortball team. There may be a number of reasons one being weight difference and workout routines. Line players can weigh as high as 400lbs. While skilled players are more athletic and less bulky able to perform tasks such as push ups or pull ups etc. 

